Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-03-24 doc/tfp-2011/main.tex
updated related work [KK]

\JoCaml\ is one of the DFLs which provides communication primitives
(like channels) for facilitating transmission of
computations. However, it does not provide ready-made language
features for fault tolerance, which is indispensable in a distributed
setting. The user has to include code for fault tolerance, as already
demonstrated in some \JoCaml\
library~\cite{mandel2008}. ML5~\cite{ML5}, a variant of ML, is a
programming language for distributed computing, specialized for web
programming. It provides primitives for transferring control between
the client and the server, as well as low-level primitives for
marshalling the data. As in the case before, ML5 is a programming
language that offers primitives for code mobility, and the code for
distribution of computation and fault-tolerance has to be included by
the user.  ML5 implements type-safe marshalling and
\functory\ does not, though an existing type-safe marshalling library
could be used with \functory. 
% Basically, the task will be transmitted
% along with the corresponding type and on unmarshalling, it could be
% matched for the correct type.
\\ \textbf{[Glasgow Distributed Haskell: TODO]}\\
CamlP3l~\cite{camlP3l} mixes the features of functional programming
with predefined patterns for parallel computation to offer a parallel
programming environment. Again, it is a programming language offering
primitives for distributing computation to parallel processes and also
to merge the results from parallel executions. Erlang~\cite{erlang}
is a programming language which has features for distribution and
fault tolerance. In particular, it has features for task distribution
and is more well-known for its rich error detection primitives and the
ability to support hot-swapping. The error detection primitives of
Erlang allow nodes to monitor processes in other nodes and also
facilitate automatic migration of tasks in failed nodes to recovered
or active nodes.

@@

\begin{comment}

% -- BELOW HERE IS OLD RELATED-WORK

Closest to the approach in this paper is Yohann Padioleau's MapReduce
implementation in \Ocaml~\cite{poor-man-mapreduce}.  It is built on
top of OCamlMPI~\cite{ocamlMPI}, while our approach uses a homemade
protocol for message passing.  Currently, we have less flexibility
w.r.t. deployment of the user program than OCamlMPI; on the other
hand, we provide a 
more generic API together with fault tolerance.  There are other
distributed computing libraries on top of which one could implement
the library discussed in this paper. \JoCaml~\cite{jocaml} is one of
them. However, \JoCaml\ does not provide fault tolerance, which is
indispensable in a distributed setting. The user has to include code
for fault tolerance, as already demonstrated in some \JoCaml\
experiments~\cite{mandel2008}.

>>>>

\JoCaml\ is one of the DFLs which provides communication primitives
(like channels) for facilitating transmission of
computations. However, it does not provide ready-made language
features for fault tolerance, which is indispensable in a distributed
setting. The user has to include code for fault tolerance, as already
demonstrated in some \JoCaml\
library~\cite{mandel2008}. ML5~\cite{ML5}, a variant of ML, is a
programming language for distributed computing, specialized for web
programming. It provides primitives for transferring control between
the client and the server, as well as low-level primitives for
marshalling the data. As in the case before, ML5 is a programming
language that offers primitives for code mobility, and the code for
distribution of computation and fault-tolerance has to be included by
the user.  ML5 implements type-safe marshalling and
\functory\ does not, though an existing type-safe marshalling library
could be used with \functory. 
% Basically, the task will be transmitted
% along with the corresponding type and on unmarshalling, it could be
% matched for the correct type.
Glasgow Distributed Haskell (GdH)~\cite{GdH} is a pure distributed
functional language that is built on top of Glasgow Haskell and
provides features for distributed computing. It is an extension of
both Glasgow Parallel Haskell, that supports only one process and
multiple threads and Concurrent Haskell that supports multiple
processes. It also offers features for fault-tolerance - error
detection and error recovery primitives in the
language.

CamlP3l~\cite{camlP3l} mixes the features of functional programming
with predefined patterns for parallel computation to offer a parallel
programming environment. Again, it is a programming language offering
primitives for distributing computation to parallel processes and also
to merge the results from parallel executions. Erlang~\cite{erlang} is
a programming language which has features for distribution and fault
tolerance. In particular, it has features for task distribution and is
more well-known for its rich error detection primitives and the
ability to support hot-swapping. The error detection primitives of
Erlang allow nodes to monitor processes in other nodes and also
facilitate automatic migration of tasks in failed nodes to recovered
or active nodes.

@@

The iTask system~\cite{iTask} is a library for the functional language
`Clean' targeted at distributed workflow management. The library
provides a set of combinator functions (some of which perform map/fold
operations) that facilitate applications running in different nodes
of a distributed system to communicate, exchange information and
coordinate their computations.

\begin{comment}
Closest to the approach in this paper is Yohann Padioleau's MapReduce
implementation in \Ocaml~\cite{poor-man-mapreduce}.  It is built on
top of OCamlMPI~\cite{ocamlMPI}, while our approach uses a homemade
protocol for message passing.  Currently, we have less flexibility
w.r.t. deployment of the user program than OCamlMPI; on the other
hand, we provide a 
more generic API together with fault tolerance.  There are other
distributed computing libraries on top of which one could implement
the library discussed in this paper. \JoCaml~\cite{jocaml} is one of
them. However, \JoCaml\ does not provide fault tolerance, which is
indispensable in a distributed setting. The user has to include code
for fault tolerance, as already demonstrated in some \JoCaml\
experiments~\cite{mandel2008}.
